---
title: "sample-r-markdown"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

```{r loading}
#load the tidyverse, but be quiet about it
options(tidyverse.quiet = TRUE) 
library(tidyverse)
library(knitr)

#load the libraries for working with the database
library(DBI)
library(RPostgreSQL)
library(getPass)
library(tidyjson)


```

## Connect to database

```{r connect}
#set the db driver to postgres, because that is what the exbuilder's database is
pgdrv <- dbDriver(drvName = "PostgreSQL")

# connect to our database
db <-DBI::dbConnect(pgdrv,
                    dbname="exbuilder",
                    host="postgres", 
                    port=5432,
                    user = 'exbuilder',
                    password = "password") # default is password

# replace password = "password" with password = getPass("Enter password: ") if you want to 
# instead enter a password. 


```

## Query the database

Once connected you can pass sql queries to the database. Don't worry about the unrecognized field error; we'll use the tidyjson library to deal with that. Note that you have to run through the experiment at least once our the query won't have any data to return. :) 

```{r query}
rawdata <- dbGetQuery(db, "SELECT * FROM experiments.runs")

```

## Turn json data into table

Next we can parse the json from our data column into trial-by-trial data

```{r jsondata}

data <- rawdata %>%
    as.tbl_json(json.column="data") %>% gather_array %>% spread_all %>%
    as_tibble() %>%
    select(!stimulus) #in jspsych this column can contain html which messes up kable


kable(head(data))

```
